The SNIK Ontology of Hospital Information Management

### 2019-03-04 paper.tex
Add todos.

\section{Architecture}\label{sec:architecture}
\todo{Describe the meta model here}
The \textbf{Semantic Network of Information Management in Hospitals} (\enquote{Krankenhaus} in German) is an OWL 2 DL ontology that consists of a central meta model and modular subontologies based on the meta model.

\section{Data Set Description}\label{sec:dsd}
The SNIK ontologies are available at \url{http://www.snik.eu/ontology/} under the Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International license.
The SNIK ontologies contain knowledge about information management in hospitals from three textbooks, an interview and a standard.
- Blue Book~\citep{bb}
- Orange Book~\citep{ob}
- CIOX
- Heinrich~\citep{he}
- IT4IT

\section{Application}\label{sec:application}
The SNIK ontologies were initially intended as the basis for a decision support system for hospital CIOs~\citep{domaene}.
While such a system was designed and a prototype was implemented, it was ultimately not integrated into the informational infrastructure of the Unilklinikum Leipzig.

- verweis auf existierende papers

>>>>

\section{Architecture}\label{sec:architecture}
\todo{Describe the meta model here}
The \textbf{Semantic Network of Information Management in Hospitals} (\enquote{Krankenhaus} in German) is an OWL 2 DL ontology that consists of a central meta model and modular subontologies. 
The SNIK ontologies contain knowledge about information management in hospitals from different sources:% three textbooks, an interview and a standard.
The textbooks \citet{bb} \citet{ob} and \citet{he} form the ontologies BB, OB and HE, respectively. 
CIOX is based on an interview with the CIO of the Universitätsklinikum Leipzig.
IT4IT is based on the IT4IT-Standard.\todo{Sebastian: Was über Standards und IT4IT schreiben}

\section{Data Set Description}\label{sec:dsd}
The SNIK ontologies are available at \url{http://www.snik.eu/ontology/} under the Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International license.

\section{Application}\label{sec:application}
The SNIK ontologies were initially intended as the basis for a decision support system for hospital CIOs~\citep{domaene}.
While such a system was designed and a prototype was implemented\todo{welches paper ist das?}, it was ultimately not integrated into the informational infrastructure of the Unilklinikum Leipzig.

\todo{verweis auf existierende papers}
\todo{benutzung durch braunschweig}
\todo{benutzung durch amsterdam}
